---
title: "Social segregation in Core Discussion Networks"
bibliography: references.bib
---

```{r globalsettings, echo=FALSE, warning=FALSE}
library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, echo=TRUE, class.source=c("test"), class.output=c("test2"))
options(width = 100)
rgl::setupKnitr()
```

```{r colorize, echo=FALSE}
colorize <- function(x, color) {
  if (knitr::is_latex_output()) {
    sprintf("\\textcolor{%s}{%s}", color, x)
  } else if (knitr::is_html_output()) {
    sprintf("<span style='color: %s;'>%s</span>", color, 
            x)
  } else x
}

```

```{css style settings, echo = FALSE}
blockquote {
    padding: 10px 20px;
    margin: 0 0 20px;
    font-size: 14px;
    border-left: 5px solid #eee;
    background-color: rgb(255,255,224,1);
}

.test {
  max-height: 300px;
  overflow-y: auto;
  overflow-x: auto;
  margin: 0px;
}

.test2 {
  max-height: 300px;
  overflow-y: auto;
  overflow-x: auto;
  margin: 0px;
  background-color: white;
  color: rgb(201, 76, 76);
}


h1, .h1, h2, .h2, h3, .h3 {
  margin-top: 24px;
}


```

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```


---


# Custom functions

- `pacage.check`: Check if packages are installed (and install if not) in R ([source](https://vbaliga.github.io/verify-that-r-packages-are-installed-and-loaded/)). 



```{r, results='hide'}
fpackage.check <- function(packages) {
  lapply(packages, FUN = function(x) {
    if (!require(x, character.only = TRUE)) {
      install.packages(x, dependencies = TRUE)
      library(x, character.only = TRUE)
    }
  })
}


```

---  

# Packages


- `tidyverse`: if you can't base them, join them  
- `haven`: because we have haven labelled vars in the dataset.  
- `Hmisc`: for weighted mean/sd  
- `plotly`: for interactive plots



```{r, results='hide'}
packages = c("tidyverse", "haven", "Hmisc", "plotly")

fpackage.check(packages)

```

--- 

# Dataset

```{r}
load(file="./data/datajt.rda")
load(file="./data/datajt_nk.rda")
```

---  

# Education {.tabset .tabset-fade}

```{r, echo=TRUE}
datajt %>% 
  filter(leeftijd>24 & !is.na(opl4)) %>%
  group_by(survey_wave, opl4) %>%
  summarise(N = n(),
            cdn_educ_EIM = mean(educ_EI, na.rm=T),
            sd = sd(educ_EI, na.rm=T),
            cdn_educ_EIM_w = wtd.mean(educ_EI, cdn_size, normwt = FALSE, na.rm = TRUE), #perhaps better to set normwt to TRUE
            sd_w = sqrt(wtd.var(educ_EI, cdn_size, normwt = FALSE, na.rm = TRUE))) %>%
  mutate(
    conf.interval = .95,
    se = sd / sqrt(N) ,
    ci = se * qt(conf.interval/2 + .5, N-1),
    se_w = sd_w / sqrt(N) , #is this correct??
    ci_w = se_w * qt(conf.interval/2 + .5, N-1)) %>%   
  na.omit() -> tgc


datajt_nk %>% 
  filter(leeftijd>24) %>%
  group_by(survey_wave, opl4) %>%
  summarise(N = n(),
            cdn_educ_EIM = mean(educ_EI, na.rm=T),
            sd = sd(educ_EI, na.rm=T)) %>%
  mutate(
    se = sd / sqrt(N) ,
    conf.interval = .95,
    ci = se * qt(conf.interval/2 + .5, N-1)) %>% 
  na.omit() -> tgc_nk


tgc$period <- as.numeric(tgc$survey_wave) + 2007
tgc$homogeneity <- round(tgc$cdn_educ_EIM, 2)
tgc$education <- as.factor(tgc$opl4)
levels(tgc$education) <- c("primary + vmbo", "havo/vwo/mbo", "hbo", "university")

tgc_nk$period <- as.numeric(tgc_nk$survey_wave) + 2007
tgc_nk$homogeneity <- round(tgc_nk$cdn_educ_EIM, 2)
tgc_nk$education <- as.factor(tgc_nk$opl4)
levels(tgc_nk$education) <- c("primary + vmbo", "havo/vwo/mbo", "hbo", "university")


datajt %>% 
  filter(leeftijd>24 & !is.na(opl4)) %>%
  group_by(survey_wave, opl4) %>%
  summarise(N = n(),
            cdn_educ_sim = mean(educ_sim, na.rm=T),
            sd = sd(educ_EI, na.rm=T),
            cdn_educ_sim_w = wtd.mean(educ_sim, cdn_size_educ, normwt = FALSE, na.rm = TRUE), #perhaps better to set normwt to TRUE
            sd_w = sqrt(wtd.var(educ_EI, cdn_size_educ, normwt = FALSE, na.rm = TRUE))) %>%
  mutate(
    conf.interval = .95,
    se = sd / sqrt(N) ,
    ci = se * qt(conf.interval/2 + .5, N-1),
    se_w = sd_w / sqrt(N) , #is this correct??
    ci_w = se_w * qt(conf.interval/2 + .5, N-1)) %>%   
  na.omit() -> tgc_op2


datajt_nk %>% 
   filter(leeftijd>24 & !is.na(opl4)) %>%
  group_by(survey_wave, opl4) %>%
  summarise(N = n(),
            cdn_educ_sim = mean(educ_sim, na.rm=T),
            sd = sd(educ_EI, na.rm=T),
            cdn_educ_sim_w = wtd.mean(educ_sim, cdn_size_educ, normwt = FALSE, na.rm = TRUE), #perhaps better to set normwt to TRUE
            sd_w = sqrt(wtd.var(educ_EI, cdn_size_educ, normwt = FALSE, na.rm = TRUE))) %>%
  mutate(
    conf.interval = .95,
    se = sd / sqrt(N) ,
    ci = se * qt(conf.interval/2 + .5, N-1),
    se_w = sd_w / sqrt(N) , #is this correct??
    ci_w = se_w * qt(conf.interval/2 + .5, N-1)) %>%   
  na.omit() -> tgc_nk_op2


tgc$period <- as.numeric(tgc$survey_wave) + 2007
tgc$homogeneity <- round(tgc$cdn_educ_EIM, 2)
tgc$education <- as.factor(tgc$opl4)
levels(tgc$education) <- c("primary + vmbo", "havo/vwo/mbo", "hbo", "university")

tgc_op2$period <- as.numeric(tgc_op2$survey_wave) + 2007
tgc_op2$homogeneity <- round(tgc_op2$cdn_educ_sim, 2)
tgc_op2$education <- as.factor(tgc_op2$opl4)
levels(tgc_op2$education) <- c("primary + vmbo", "havo/vwo/mbo", "hbo", "university")

tgc_nk$period <- as.numeric(tgc_nk$survey_wave) + 2007
tgc_nk$homogeneity <- round(tgc_nk$cdn_educ_EIM, 2)
tgc_nk$education <- as.factor(tgc_nk$opl4)
levels(tgc_nk$education) <- c("primary + vmbo", "havo/vwo/mbo", "hbo", "university")

tgc_nk_op2$period <- as.numeric(tgc_nk_op2$survey_wave) + 2007
tgc_nk_op2$homogeneity <- round(tgc_nk_op2$cdn_educ_sim, 2)
tgc_nk_op2$education <- as.factor(tgc_nk_op2$opl4)
levels(tgc_nk_op2$education) <- c("primary + vmbo", "havo/vwo/mbo", "hbo", "university")



``` 

## all


```{r}

plot <- ggplot(tgc, aes(x=period, y=homogeneity, colour=education)) + 
  geom_line(position=position_dodge(0.1)) +
  geom_errorbar(aes(ymin=homogeneity-ci, ymax=homogeneity+ci), width=.6, position=position_dodge(0.1)) +
  geom_point(position=position_dodge(0.1)) + 
  scale_x_continuous(breaks = 2008:2021, limits = c(2007, 2022), labels = as.character(c(2008:2021))) +
  scale_y_continuous(breaks = c(-1, -0.75, -.5, -.25, 0, .25, .5, .75, 1), limits = c(-1,1)) + 
  labs(title = "Educational homogeneity in CDN", caption = "Note: 95% CI \n Source: CentERdata 2021", 
       y = "EI-index", x="period") + 
  scale_colour_hue(name="education ego",    # Legend label, use darker colors
                   #breaks=c("1", "2", "3", "4"),
                   #labels=c("primary + vmbo", "havo/vwo/mbo", "hbo", "university"),
                   l=40)       +              # Use darker colors, lightness=40
  theme(axis.text.x = element_text(angle=45),
        legend.justification=c(1,0),
        legend.position="right")  



#plot
ggplotly(plot) %>%
  layout(margin = list(b=100), annotations = list(x=2021, y = -1.1, showarrow = F, font = list(size=10), text="\n \n  \n  \n \n \n \n \n \n Note: 95% CI \n Source: CentERdata 2021"))



```
<br> 

Significance of trend: 

- negative trend of 'primary + vmbo' and 'havo/vwo/mbo'  
- positive trend of 'university' 


```{r}
datajt %>% 
  filter(leeftijd>24 & !is.na(opl4)) %>%
  with(lm(educ_EI ~ as.factor(opl4) + as.numeric(survey_wave):as.factor(opl4) )) %>% 
  summary()

```

--- 

## no kin 


```{r}

plot <- ggplot(tgc_nk, aes(x=period, y=homogeneity, colour=education)) + 
  geom_line(position=position_dodge(0.1)) +
  geom_errorbar(aes(ymin=homogeneity-ci, ymax=homogeneity+ci), width=.6, position=position_dodge(0.1)) +
  geom_point(position=position_dodge(0.1)) + 
  scale_x_continuous(breaks = 2008:2021, limits = c(2007, 2022), labels = as.character(c(2008:2021))) +
  scale_y_continuous(breaks = c(-1, -0.75, -.5, -.25, 0, .25, .5, .75, 1), limits = c(-1,1)) + 
  labs(title = "Educational homogeneity in CDN", caption = "Note: 95% CI \n Source: CentERdata 2021", 
       y = "EI-index", x="period") + 
  scale_colour_hue(name="education ego",    # Legend label, use darker colors
                   #breaks=c("1", "2", "3", "4"),
                   #labels=c("primary + vmbo", "havo/vwo/mbo", "hbo", "university"),
                   l=40)       +              # Use darker colors, lightness=40
  theme(axis.text.x = element_text(angle=45),
        legend.justification=c(1,0),
        legend.position="right")  


#plot
#plot
ggplotly(plot) %>%
  layout(margin = list(b=100), annotations = list(x=2021, y = -1.1, showarrow = F, font = list(size=10), text="\n \n  \n  \n  \n \n \n \n \n Note: 95% CI \n Source: CentERdata 2021"))



```

---  


## all (similarity)


```{r}
#hist(datajt$educ_sim)


plot <- ggplot(tgc_op2, aes(x=period, y=homogeneity, colour=education)) + 
  geom_line(position=position_dodge(0.1)) +
  geom_errorbar(aes(ymin=homogeneity-ci, ymax=homogeneity+ci), width=.6, position=position_dodge(0.1)) +
  geom_point(position=position_dodge(0.1)) + 
  scale_x_continuous(breaks = 2008:2021, limits = c(2007, 2022), labels = as.character(c(2008:2021))) +
  scale_y_continuous(breaks = c(-1, -0.75, -.5, -.25, 0, .25, .5, .75, 1), limits = c(-1,1)) + 
  labs(title = "Educational homogeneity in CDN", caption = "Note: 95% CI \n Source: CentERdata 2021", 
       y = "S-index", x="period") + 
  scale_colour_hue(name="education ego",    # Legend label, use darker colors
                   #breaks=c("1", "2", "3", "4"),
                   #labels=c("primary + vmbo", "havo/vwo/mbo", "hbo", "university"),
                   l=40)       +              # Use darker colors, lightness=40
  theme(axis.text.x = element_text(angle=45),
        legend.justification=c(1,0),
        legend.position="right")  



#plot
ggplotly(plot) %>%
  layout(margin = list(b=100), annotations = list(x=2021, y = -1.1, showarrow = F, font = list(size=10), text="\n \n  \n \n \n \n \n \n \n Note: 95% CI \n Source: CentERdata 2021"))



```

---

## no kin (similarity)


```{r}



plot <- ggplot(tgc_nk_op2, aes(x=period, y=homogeneity, colour=education)) + 
  geom_line(position=position_dodge(0.1)) +
  geom_errorbar(aes(ymin=homogeneity-ci, ymax=homogeneity+ci), width=.6, position=position_dodge(0.1)) +
  geom_point(position=position_dodge(0.1)) + 
  scale_x_continuous(breaks = 2008:2021, limits = c(2007, 2022), labels = as.character(c(2008:2021))) +
  scale_y_continuous(breaks = c(-1, -0.75, -.5, -.25, 0, .25, .5, .75, 1), limits = c(-1,1)) + 
  labs(title = "Educational homogeneity in CDN", caption = "Note: 95% CI \n Source: CentERdata 2021", 
       y = "S-index", x="period") + 
  scale_colour_hue(name="education ego",    # Legend label, use darker colors
                   #breaks=c("1", "2", "3", "4"),
                   #labels=c("primary + vmbo", "havo/vwo/mbo", "hbo", "university"),
                   l=40)       +              # Use darker colors, lightness=40
  theme(axis.text.x = element_text(angle=45),
        legend.justification=c(1,0),
        legend.position="right")  



#plot
ggplotly(plot) %>%
  layout(margin = list(b=100), annotations = list(x=2021, y = -1.1, showarrow = F, font = list(size=10), text="\n \n  \n  \n \n \n \n \n \n Note: 95% CI \n Source: CentERdata 2021"))



```

---  



# Gender {.tabset .tabset-fade}


```{r, echo=TRUE}
datajt %>% 
  filter(cdn_size>0 & !is.na(geslacht)) %>%
  group_by(survey_wave, geslacht) %>%
  summarise(N = n(),
            gender_EI_mean = mean(gender_EI, na.rm=T),
            sd = sd(gender_EI, na.rm=T)) %>%
  mutate(
    se = sd / sqrt(N) ,
    conf.interval = .95,
    ci = se * qt(conf.interval/2 + .5, N-1)) -> tgc

tgc$period <- as.numeric(tgc$survey_wave) + 2007
tgc$homogeneity <- round(tgc$gender_EI_mean, 2)
tgc$gender <- as.factor(tgc$geslacht)
levels(tgc$gender) <- c("male", "female")

datajt_nk %>% 
  filter(cdn_size>0 & !is.na(geslacht)) %>%
  group_by(survey_wave, geslacht) %>%
  summarise(N = n(),
            gender_EI_mean = mean(gender_EI, na.rm=T),
            sd = sd(gender_EI, na.rm=T)) %>%
  mutate(
    se = sd / sqrt(N) ,
    conf.interval = .95,
    ci = se * qt(conf.interval/2 + .5, N-1)) -> tgc_nk

tgc_nk$period <- as.numeric(tgc_nk$survey_wave) + 2007
tgc_nk$homogeneity <- round(tgc_nk$gender_EI_mean, 2)
tgc_nk$gender <- as.factor(tgc_nk$geslacht)
levels(tgc_nk$gender) <- c("male", "female")



```


## all
```{r}

plot <- ggplot(tgc, aes(x=period, y=homogeneity, colour=gender)) + 
  geom_line(position=position_dodge(0.1)) +
  geom_errorbar(aes(ymin=homogeneity-ci, ymax=homogeneity+ci), width=.6, position=position_dodge(0.1)) +
  geom_point(position=position_dodge(0.1)) + 
  scale_x_continuous(breaks = 2008:2021, limits = c(2007,2022), labels = as.character(c(2008:2021))) +
  scale_y_continuous(breaks = c(-1, -0.75, -.5, -.25, 0, .25, .5, .75, 1), limits = c(-1,1)) + 
  labs(title = "Gender homogeneity in CDN", caption = "Note: 95% CI \n Source: CentERdata 2021", 
       y = "EI-index", x="period") + 
  scale_colour_hue(name="gender ego",    # Legend label, use darker colors
                   #breaks=c("2", "1"),
                   #labels=c("female", "male"),
                   l=40)       +              # Use darker colors, lightness=40
  theme(axis.text.x = element_text(angle=45),
        legend.justification=c(1,0),
        legend.position="right")  

ggplotly(plot) %>%
  layout(margin = list(b=100), annotations = list(x=2021, y = -1, showarrow = F, font = list(size=10), text="\n \n \n \n \n  \n  \n \n \n \n \n Note: 95% CI \n Source: CentERdata 2021"))

```

---  


## no kin
```{r}

plot <- ggplot(tgc_nk, aes(x=period, y=homogeneity, colour=gender)) + 
  geom_line(position=position_dodge(0.1)) +
  geom_errorbar(aes(ymin=homogeneity-ci, ymax=homogeneity+ci), width=.6, position=position_dodge(0.1)) +
  geom_point(position=position_dodge(0.1)) + 
  scale_x_continuous(breaks = 2008:2021, limits = c(2007,2022), labels = as.character(c(2008:2021))) +
  scale_y_continuous(breaks = c(-1, -0.75, -.5, -.25, 0, .25, .5, .75, 1), limits = c(-1,1)) + 
  labs(title = "Gender homogeneity in CDN", caption = "Note: 95% CI \n Source: CentERdata 2021", 
       y = "EI-index", x="period") + 
  scale_colour_hue(name="gender ego",    # Legend label, use darker colors
                   #breaks=c("2", "1"),
                   #labels=c("female", "male"),
                   l=40)       +              # Use darker colors, lightness=40
  theme(axis.text.x = element_text(angle=45),
        legend.justification=c(1,0),
        legend.position="right")  

ggplotly(plot) %>%
  layout(margin = list(b=100), annotations = list(x=2021, y = -1, showarrow = F, font = list(size=10), text="\n \n \n \n  \n \n \n \n \n \n \n Note: 95% CI \n Source: CentERdata 2021"))

```
<br>

---   



# Age {.tabset .tabset-fade}


```{r}

datajt %>% 
  filter(!is.na(leeftijd) & leeftijd>15) %>%
  group_by(survey_wave, leeftijd_cat13) %>%
  summarise(N = n(),
            cdn_leeftijd_EIM = mean(leeftijd_EI, na.rm=T),
            sd = sd(leeftijd_EI, na.rm=T),
            cdn_leeftijd_EIM_w = wtd.mean(leeftijd_EI, cdn_size_age, normwt = FALSE, na.rm = TRUE), #perhaps better to set normwt to TRUE
            sd_w = sqrt(wtd.var(leeftijd_EI, cdn_size_age, normwt = FALSE, na.rm = TRUE))) %>%
  mutate(
    conf.interval = .95,
    se = sd / sqrt(N) ,
    ci = se * qt(conf.interval/2 + .5, N-1),
    se_w = sd_w / sqrt(N) , #is this correct??
    ci_w = se_w * qt(conf.interval/2 + .5, N-1)) %>%   
  na.omit() -> tgc



datajt_nk %>% 
  filter(!is.na(leeftijd) & leeftijd>15) %>%
  group_by(survey_wave, leeftijd_cat13) %>%
  summarise(N = n(),
            cdn_leeftijd_EIM = mean(leeftijd_EI, na.rm=T),
            sd = sd(leeftijd_EI, na.rm=T),
            cdn_leeftijd_EIM_w = wtd.mean(leeftijd_EI, cdn_size, normwt = FALSE, na.rm = TRUE), #perhaps better to set normwt to TRUE
            sd_w = sqrt(wtd.var(leeftijd_EI, cdn_size, normwt = FALSE, na.rm = TRUE))) %>%
  mutate(
    conf.interval = .95,
    se = sd / sqrt(N) ,
    ci = se * qt(conf.interval/2 + .5, N-1),
    se_w = sd_w / sqrt(N) , #is this correct??
    ci_w = se_w * qt(conf.interval/2 + .5, N-1)) %>%   
  na.omit() -> tgc_nk


test <- cut(as.numeric(datajt$leeftijd),breaks = c(-Inf, 15, 20, 25, 30, 35, 40,45,50,55,60,65,70, Inf))
#levels(test)


tgc$period <- as.numeric(tgc$survey_wave) + 2007
tgc$homogeneity <- round(tgc$cdn_leeftijd_EIM, 2)
tgc$age <- as.factor(tgc$leeftijd_cat13)
levels(tgc$age) <- levels(test)[-1]


tgc_nk$period <- as.numeric(tgc_nk$survey_wave) + 2007
tgc_nk$homogeneity <- round(tgc_nk$cdn_leeftijd_EIM, 2)
tgc_nk$age <- as.factor(tgc_nk$leeftijd_cat13)
levels(tgc_nk$age) <- levels(test)[-1]

datajt %>% 
  filter(!is.na(leeftijd) & leeftijd>15) %>%
  group_by(survey_wave, leeftijd_cat13) %>%
  summarise(N = n(),
            cdn_leeftijd_EIM = mean(leeftijd_sim, na.rm=T),
            sd = sd(leeftijd_sim, na.rm=T),
            cdn_leeftijd_EIM_w = wtd.mean(leeftijd_sim, cdn_size_age, normwt = FALSE, na.rm = TRUE), #perhaps better to set normwt to TRUE
            sd_w = sqrt(wtd.var(leeftijd_sim, cdn_size_age, normwt = FALSE, na.rm = TRUE))) %>%
  mutate(
    conf.interval = .95,
    se = sd / sqrt(N) ,
    ci = se * qt(conf.interval/2 + .5, N-1),
    se_w = sd_w / sqrt(N) , #is this correct??
    ci_w = se_w * qt(conf.interval/2 + .5, N-1)) %>%   
  na.omit() -> tgc_op2



datajt_nk %>% 
  filter(!is.na(leeftijd) & leeftijd>15) %>%
  group_by(survey_wave, leeftijd_cat13) %>%
  summarise(N = n(),
            cdn_leeftijd_EIM = mean(leeftijd_sim, na.rm=T),
            sd = sd(leeftijd_sim, na.rm=T),
            cdn_leeftijd_EIM_w = wtd.mean(leeftijd_sim, cdn_size_age, normwt = FALSE, na.rm = TRUE), #perhaps better to set normwt to TRUE
            sd_w = sqrt(wtd.var(leeftijd_sim, cdn_size_age, normwt = FALSE, na.rm = TRUE))) %>%
  mutate(
    conf.interval = .95,
    se = sd / sqrt(N) ,
    ci = se * qt(conf.interval/2 + .5, N-1),
    se_w = sd_w / sqrt(N) , #is this correct??
    ci_w = se_w * qt(conf.interval/2 + .5, N-1)) %>%   
  na.omit() -> tgc_nk_op2


test <- cut(as.numeric(datajt$leeftijd),breaks = c(-Inf, 15, 20, 25, 30, 35, 40,45,50,55,60,65,70, Inf))
#levels(test)


tgc_op2$period <- as.numeric(tgc_op2$survey_wave) + 2007
tgc_op2$homogeneity <- round(tgc_op2$cdn_leeftijd_EIM, 2)
tgc_op2$age <- as.factor(tgc_op2$leeftijd_cat13)
levels(tgc_op2$age) <- levels(test)[-1]


tgc_nk_op2$period <- as.numeric(tgc_nk_op2$survey_wave) + 2007
tgc_nk_op2$homogeneity <- round(tgc_nk_op2$cdn_leeftijd_EIM, 2)
tgc_nk_op2$age <- as.factor(tgc_nk_op2$leeftijd_cat13)
levels(tgc_nk_op2$age) <- levels(test)[-1]





```

## all
```{r}


plot <- ggplot(tgc, aes(x=period, y=homogeneity, colour=age)) + 
  geom_line(position=position_dodge(0.1)) +
  geom_errorbar(aes(ymin=homogeneity-ci, ymax=homogeneity+ci), width=.6, position=position_dodge(0.1)) +
  geom_point(position=position_dodge(0.1)) + 
  scale_x_continuous(breaks = 2008:2021, limits = c(2007,2022), labels = as.character(c(2008:2021))) +
  scale_y_continuous(breaks = c(-1, -0.75, -.5, -.25, 0, .25, .5, .75, 1), limits = c(-1,1)) + 
  labs(title = "Age homogeneity", caption = "Note: 95% CI \n Source: CentERdata 2021", 
       y = "EI-index", x="period") + 
  scale_colour_hue(name="age ego",    # Legend label, use darker colors
                   #breaks=c("1", "2"),
                   #labels=levels(test),
                   l=40)       +              # Use darker colors, lightness=40
  theme(axis.text.x = element_text(angle=45),
        legend.justification=c(1,0),
        legend.position="right")  

ggplotly(plot) %>%
  layout(margin = list(b=100), annotations = list(x=2021, y = -1, showarrow = F, font = list(size=10), text="\n \n \n \n  \n \n  \n \n \n \n \n Note: 95% CI \n Source: CentERdata 2021"))
```
<br>

---  

## no kin 

```{r}


plot <- ggplot(tgc_nk, aes(x=period, y=homogeneity, colour=age)) + 
  geom_line(position=position_dodge(0.1)) +
  geom_errorbar(aes(ymin=homogeneity-ci, ymax=homogeneity+ci), width=.6, position=position_dodge(0.1)) +
  geom_point(position=position_dodge(0.1)) + 
  scale_x_continuous(breaks = 2008:2021, limits = c(2007,2022), labels = as.character(c(2008:2021))) +
  scale_y_continuous(breaks = c(-1, -0.75, -.5, -.25, 0, .25, .5, .75, 1), limits = c(-1,1)) + 
  labs(title = "Age homogeneity", caption = "Note: 95% CI \n Source: CentERdata 2021", 
       y = "EI-index", x="period") + 
  scale_colour_hue(name="age ego",    # Legend label, use darker colors
                   #breaks=c("1", "2"),
                   #labels=levels(test),
                   l=40)       +              # Use darker colors, lightness=40
  theme(axis.text.x = element_text(angle=45),
        legend.justification=c(1,0),
        legend.position="right")  
#plot
ggplotly(plot) %>%
  layout(margin = list(b=100), annotations = list(x=2021, y = -1, showarrow = F, font = list(size=10), text="\n \n \n \n  \n  \n \n \n \n \n \n Note: 95% CI \n Source: CentERdata 2021"))
```
<br> 

---  

## all (similarity)
```{r}


plot <- ggplot(tgc_op2, aes(x=period, y=homogeneity, colour=age)) + 
  geom_line(position=position_dodge(0.1)) +
  geom_errorbar(aes(ymin=homogeneity-ci, ymax=homogeneity+ci), width=.6, position=position_dodge(0.1)) +
  geom_point(position=position_dodge(0.1)) + 
  scale_x_continuous(breaks = 2008:2021, limits = c(2007,2022), labels = as.character(c(2008:2021))) +
  scale_y_continuous(breaks = c(-1, -0.75, -.5, -.25, 0, .25, .5, .75, 1), limits = c(-1,1))+ 
  labs(title = "Age homogeneity", caption = "Note: 95% CI \n Source: CentERdata 2021", 
       y = "S-index", x="period") + 
  scale_colour_hue(name="age ego",    # Legend label, use darker colors
                   #breaks=c("1", "2"),
                   #labels=levels(test),
                   l=40)       +              # Use darker colors, lightness=40
  theme(axis.text.x = element_text(angle=45),
        legend.justification=c(1,0),
        legend.position="right")  

ggplotly(plot) %>%
  layout(margin = list(b=100), annotations = list(x=2021, y = -1, showarrow = F, font = list(size=10), text="\n \n \n \n  \n  \n \n \n \n \n \n Note: 95% CI \n Source: CentERdata 2021"))
```
<br>

---  

## no kin (similarity)
```{r}


plot <- ggplot(tgc_nk_op2, aes(x=period, y=homogeneity, colour=age)) + 
  geom_line(position=position_dodge(0.1)) +
  geom_errorbar(aes(ymin=homogeneity-ci, ymax=homogeneity+ci), width=.6, position=position_dodge(0.1)) +
  geom_point(position=position_dodge(0.1)) + 
  scale_x_continuous(breaks = 2008:2021, limits = c(2007,2022), labels = as.character(c(2008:2021))) +
  scale_y_continuous(breaks = c(-1, -0.75, -.5, -.25, 0, .25, .5, .75, 1), limits = c(-1,1)) + 
  labs(title = "Age homogeneity", caption = "Note: 95% CI \n Source: CentERdata 2021", 
       y = "S-index", x="period") + 
  scale_colour_hue(name="age ego",    # Legend label, use darker colors
                   #breaks=c("1", "2"),
                   #labels=levels(test),
                   l=40)       +              # Use darker colors, lightness=40
  theme(axis.text.x = element_text(angle=45),
        legend.justification=c(1,0),
        legend.position="right")  

ggplotly(plot) %>%
  layout(margin = list(b=100), annotations = list(x=2021, y = -1, showarrow = F, font = list(size=10), text="\n \n \n \n  \n \n  \n \n \n \n \n Note: 95% CI \n Source: CentERdata 2021"))
```
<br> 

--- 

# Ethnicity {.tabset .tabset-fade}


```{r}

datajt %>% 
  filter(!is.na(etni3)) %>%
  group_by(survey_wave, etni3) %>%
  summarise(N = n(),
            cdn_etni_EIM = mean(etni_EI, na.rm=T),
            sd = sd(etni_EI, na.rm=T),
            cdn_etni_EIM_w = wtd.mean(etni_EI, cdn_size, normwt = FALSE, na.rm = TRUE), #perhaps better to set normwt to TRUE
            sd_w = sqrt(wtd.var(etni_EI, cdn_size, normwt = FALSE, na.rm = TRUE))) %>%
  mutate(
    conf.interval = .95,
    se = sd / sqrt(N) ,
    ci = se * qt(conf.interval/2 + .5, N-1),
    se_w = sd_w / sqrt(N) , #is this correct??
    ci_w = se_w * qt(conf.interval/2 + .5, N-1)) %>%   
  na.omit() -> tgc

datajt_nk %>% 
  filter(!is.na(etni3)) %>%
  group_by(survey_wave, etni3) %>%
  summarise(N = n(),
            cdn_etni_EIM = mean(etni_EI, na.rm=T),
            sd = sd(etni_EI, na.rm=T),
            cdn_etni_EIM_w = wtd.mean(etni_EI, cdn_size, normwt = FALSE, na.rm = TRUE), #perhaps better to set normwt to TRUE
            sd_w = sqrt(wtd.var(etni_EI, cdn_size, normwt = FALSE, na.rm = TRUE))) %>%
  mutate(
    conf.interval = .95,
    se = sd / sqrt(N) ,
    ci = se * qt(conf.interval/2 + .5, N-1),
    se_w = sd_w / sqrt(N) , #is this correct??
    ci_w = se_w * qt(conf.interval/2 + .5, N-1)) %>%   
  na.omit() -> tgc_nk




tgc$period <- as.numeric(tgc$survey_wave) + 2007
tgc$homogeneity <- round(tgc$cdn_etni_EIM, 2)
tgc$ethnicity <- as.factor(tgc$etni3)
levels(tgc$ethnicity) <- c("Dutch", "Western", "non-Western")

tgc_nk$period <- as.numeric(tgc_nk$survey_wave) + 2007
tgc_nk$homogeneity <- round(tgc_nk$cdn_etni_EIM, 2)
tgc_nk$ethnicity <- as.factor(tgc_nk$etni3)
levels(tgc_nk$ethnicity) <- c("Dutch", "Western", "non-Western")

```

## all

```{r}
plot <- ggplot(tgc, aes(x=period, y=homogeneity, colour=ethnicity)) + 
  geom_line(position=position_dodge(0.1)) +
  geom_errorbar(aes(ymin=homogeneity-ci, ymax=homogeneity+ci), width=.6, position=position_dodge(0.1)) +
  geom_point(position=position_dodge(0.1)) + 
  scale_x_continuous(breaks = 2011:2021, limits = c(2010,2022), labels = as.character(c(2011:2021))) +
  scale_y_continuous(breaks = c(-1, -0.75, -.5, -.25, 0, .25, .5, .75, 1), limits = c(-1,1)) + 
  labs(title = "Ethnic homogeneity", caption = "Note: 95% CI \n Source: CentERdata 2021", 
       y = "EI-index", x="period") + 
  scale_colour_hue(name="ethnicity ego",    # Legend label, use darker colors
                   #breaks=c("1", "2"),
                   #labels=c("D", "W", "NW"),
                   l=40)       +              # Use darker colors, lightness=40
  theme(axis.text.x = element_text(angle=45),
        legend.justification=c(1,0),
        legend.position="right")  

ggplotly(plot) %>%
  layout(margin = list(b=100), annotations = list(x=2021, y = -1, showarrow = F, font = list(size=10), text="\n \n \n \n  \n  \n \n \n \n \n \n Note: 95% CI \n Source: CentERdata 2021"))
```

<br> 

---  

## no kin

```{r}
plot <- ggplot(tgc_nk, aes(x=period, y=homogeneity, colour=ethnicity)) + 
  geom_line(position=position_dodge(0.1)) +
  geom_errorbar(aes(ymin=homogeneity-ci, ymax=homogeneity+ci), width=.6, position=position_dodge(0.1)) +
  geom_point(position=position_dodge(0.1)) + 
  scale_x_continuous(breaks = 2011:2021, limits = c(2010,2022), labels = as.character(c(2011:2021))) +
  scale_y_continuous(breaks = c(-1, -0.75, -.5, -.25, 0, .25, .5, .75, 1), limits = c(-1,1)) + 
  labs(title = "Ethnic homogeneity", caption = "Note: 95% CI \n Source: CentERdata 2021", 
       y = "EI-index", x="period") + 
  scale_colour_hue(name="ethnicity ego",    # Legend label, use darker colors
                   #breaks=c("1", "2"),
                   #labels=c("D", "W", "NW"),
                   l=40)       +              # Use darker colors, lightness=40
  theme(axis.text.x = element_text(angle=45),
        legend.justification=c(1,0),
        legend.position="right")  

ggplotly(plot) %>%
  layout(margin = list(b=100), annotations = list(x=2021, y = -1, showarrow = F, font = list(size=10), text="\n \n \n \n  \n \n \n \n \n \n \n Note: 95% CI \n Source: CentERdata 2021"))
```

<br> 

---  



# Take Home Message  

- Pronounced segregation in all social dimensions.  
- Overall, segregation in social networks is quite constant over time  
- Age segregation is increasing (for the elderly)  
- Educational segregation is increasing (for the higher educated)  


---  

