---
title: "Social segregation"
---

```{r globalsettings, echo=FALSE, warning=FALSE}
library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, echo=FALSE, class.source=c("test"), class.output=c("test2"))
options(width = 100)
rgl::setupKnitr()
```

```{r colorize, echo=FALSE}
colorize <- function(x, color) {
  if (knitr::is_latex_output()) {
    sprintf("\\textcolor{%s}{%s}", color, x)
  } else if (knitr::is_html_output()) {
    sprintf("<span style='color: %s;'>%s</span>", color, 
            x)
  } else x
}

```

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```


---


#  Intro


This [website](https://jochemtolsma.github.io/JCA/) is a replication package for the presentation at JCA by @Tolsma2022.

It contains R code to replicate all the Figures.

To copy the code click the button in the upper right corner of the code-chunks.

Use the top menu to navigate to the section of interest. 

The source code of this website can be found on [Github](https://github.com/JochemTolsma/JCA)

Questions can be addressed to [Jochem Tolsma](mailto:jochem.tolsma@ru.nl).


**A big *Thank You* to `r colorize("Thijmen Jeroense", "red") for preparing the LISS data!**  

---  





```{r, echo=FALSE, results='hide'}
fpackage.check <- function(packages) {
  lapply(packages, FUN = function(x) {
    if (!require(x, character.only = TRUE)) {
      install.packages(x, dependencies = TRUE)
      library(x, character.only = TRUE)
    }
  })
}

packages = c("VennDiagram", "EnvStats")

fpackage.check(packages)
```







# Introduction 

- My chair, supported by the James Coleman Association, has the title: **Social Divisions Between Groups**. 


```{r, fig.cap="Fig 1. Social Divisions Between Groups"}

# create Venn diagram with three sets
v <- draw.triple.venn(area1=40, area2=40, area3=40,
				n12=10, n23=10, n13=10, n123=5,
				category=c("Inequality","Polarization", "segregation"), cat.dist = -.1, cat.cex=1.5,
				col="Red",fill=c("Green","Yellow","Blue"),
				lwd=3,
				alpha = .3,
				label.col = "dark red",
				cex=1.2,
				lty=2, 
				ind = FALSE)

#lapply(v, names)
#lapply(v, function(i) i$label)
v[[7]]$label <- ""
v[[8]]$label <- ""
v[[9]]$label <- ""
v[[10]]$label <- ""
v[[11]]$label <- "Social Divisions \n Between Groups"
v[[12]]$label <- ""
v[[13]]$label <- ""

grid.newpage()
grid.draw(v)
grid.newpage()

```

---  

# Inequality

The unequal distribution of resources. 

<iframe src="https://jtolsma.shinyapps.io/Gini2/" height="405" width="720" style="border: 1px solid #464646;" allowfullscreen="" allow="autoplay"></iframe>

---  

# Polarization

The unequal distribution of opinions. 


```{r}
set.seed(1234)

dat <- data.frame(group = factor(rep(c("group A","group B"), each=200)), 
                   opinion = c(rnormTrunc(200, mean = 1, sd = 1, min = 0, max = 7),rnormTrunc(200, mean = 6, sd = 1, min = 0, max = 7)))
 
# Density plots with semi-transparent fill
ggplot(dat, aes(x=opinion, fill=group)) +
  geom_density(alpha=.3, kernel="o") +
  scale_x_continuous(breaks = 0:7, limits = c(-1,8) , labels = c("totally disagree", "", "","", "", "", "", "totally agree")) 
```


--- 


# Segregation

The unequal distribution of positions. 

## Segregation along different social dimensions

* Class  
* Religion  
* Ethnicity  
* Age  
* Gender  
* Education  

## Segregation in differnt social contexts. 

* Geographical areas  
* Schools  
* Work  
* Social Networks  

# Why segregation?  

- We don't much about segregation:  
  * Is it increasing or decreasing over time?  
  * Along which social dimension is segregation most prominent?  
  * Within which social context is segregation most prominent?  
  * Is segregation mainly the result of polarization and inequality or the cause for polarization and inequality?  
  * Do we need to take action and through which policies? 

---  


# References
