---
title: "Social segregation in Core Discussion Networks"
---

```{r globalsettings, echo=FALSE, warning=FALSE}
library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, echo=FALSE, class.source=c("test"), class.output=c("test2"))
options(width = 100)
rgl::setupKnitr()
```

```{r colorize, echo=FALSE}
colorize <- function(x, color) {
  if (knitr::is_latex_output()) {
    sprintf("\\textcolor{%s}{%s}", color, x)
  } else if (knitr::is_html_output()) {
    sprintf("<span style='color: %s;'>%s</span>", color, 
            x)
  } else x
}

```

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```


---


# Custom functions

- `pacage.check`: Check if packages are installed (and install if not) in R ([source](https://vbaliga.github.io/verify-that-r-packages-are-installed-and-loaded/)). 



```{r, results='hide'}
fpackage.check <- function(packages) {
  lapply(packages, FUN = function(x) {
    if (!require(x, character.only = TRUE)) {
      install.packages(x, dependencies = TRUE)
      library(x, character.only = TRUE)
    }
  })
}


```

---  

# Packages


- `tidyverse`: if you can't base them, join them  
- `haven`: because we have haven labelled vars in the dataset.  
- `Hmisc`: for weighted mean/sd  
- `plotly`: for interactive plots



```{r, results='hide'}
packages = c("tidyverse", "haven", "Hmisc", "plotly")

fpackage.check(packages)

```

--- 

# Dataset

```{r}
#load(file="./data/liss_merged_core_file_v3_0921.Rdata")
load(file="./data/datajt.rda")
load(file="./data/datajt_nk.rda")
```


# Education {.tabset .tabset-fade}

```{r}

datajt %>% 
  group_by(survey_wave, opl4) %>%
  summarise(N = n(),
            cdn_sizeM = mean(cdn_size, na.rm=T),
            sd = sd(cdn_size, na.rm=T)) %>%
  mutate(
    se = sd / sqrt(N) ,
    conf.interval = .95,
    ci = se * qt(conf.interval/2 + .5, N-1)) %>% 
  na.omit() -> tgc


ggplot(tgc, aes(x=as.numeric(survey_wave), y=cdn_sizeM, colour=as.factor(opl4))) + 
    geom_errorbar(aes(ymin=cdn_sizeM-ci, ymax=cdn_sizeM+ci), width=.6, position=position_dodge(0.1)) +
    geom_line(position=position_dodge(0.1)) +
    geom_point(position=position_dodge(0.1)) + 
    scale_x_continuous(breaks = 1:14, limits = c(0,15) , labels = as.character(c(2008:2021))) +
    scale_y_continuous(breaks = 1:5, limits = c(1,4)) + 
    labs(title = "CDN-size per education", caption = "Note: 95% CI \n Source: CentERdata 2021", 
       y = "CDN size", x="period") + 
    scale_colour_hue(name="education ego",    # Legend label, use darker colors
                     breaks=c("1", "2", "3", "4"),
                     labels=c("primary + vmbo", "havo/vwo/mbo", "hbo", "university"),
                     l=40)       +              # Use darker colors, lightness=40
    theme(legend.justification=c(1,0),
          legend.position=c("right"))  
```

# Gender {.tabset .tabset-fade}

```{r}

datajt %>% 
  group_by(survey_wave, geslacht) %>%
  summarise(N = n(),
            cdn_sizeM = mean(cdn_size, na.rm=T),
            sd = sd(cdn_size, na.rm=T)) %>%
  mutate(
    se = sd / sqrt(N) ,
    conf.interval = .95,
    ci = se * qt(conf.interval/2 + .5, N-1)) %>% 
  na.omit() -> tgc



ggplot(tgc, aes(x=as.numeric(survey_wave), y=cdn_sizeM, colour=as.factor(geslacht))) + 
    geom_errorbar(aes(ymin=cdn_sizeM-ci, ymax=cdn_sizeM+ci), width=.6, position=position_dodge(0.1)) +
    geom_line(position=position_dodge(0.1)) +
    geom_point(position=position_dodge(0.1)) + 
    scale_x_continuous(breaks = 1:14, limits = c(0,15) , labels = as.character(c(2008:2021))) +
    scale_y_continuous(breaks = 1:5, limits = c(1,4)) + 
    labs(title = "CDN-size per gender", caption = "Note: 95% CI \n Source: CentERdata 2021", 
       y = "CDN size", x="period") + 
    scale_colour_hue(name="gender ego",    # Legend label, use darker colors
                     breaks=c("2", "1"),
                     labels=c("female", "male"),
                     l=40)       +                # Use darker colors, lightness=40
    theme(legend.justification=c(1,0),
          legend.position=c("right"))  
```

# Age {.tabset .tabset-fade}

```{r}

datajt %>% 
  group_by(survey_wave, leeftijd_cat13) %>%
  summarise(N = n(),
            cdn_sizeM = mean(cdn_size, na.rm=T),
            sd = sd(cdn_size, na.rm=T)) %>%
  mutate(
    se = sd / sqrt(N) ,
    conf.interval = .95,
    ci = se * qt(conf.interval/2 + .5, N-1)) %>% 
  na.omit() -> tgc

tgc$period <- as.numeric(tgc$survey_wave) + 2007
tgc$size <- round(tgc$cdn_sizeM, 2)
tgc$age <- as.factor(tgc$leeftijd_cat13)
levels(tgc$age) <- levels(test)



plot <- ggplot(tgc, aes(x=period, y=size, colour=age)) +
    geom_line() +
    geom_errorbar(aes(ymin=cdn_sizeM-ci, ymax=cdn_sizeM+ci), width=.6, position=position_dodge(0.1)) 
    
ggplotly(plot)     

plot
ggplotly(plot) %>%
  layout(annotations = list(x=1, y = - 0.1, showarrow = F, text="THE CAPTION"))



plot <- ggplot(tgc, aes(x=period, y=size, colour=age)) + 
  geom_line(position=position_dodge(0.1), aes(color=age)) +  
  geom_errorbar(aes(ymin=cdn_sizeM-ci, ymax=cdn_sizeM+ci), width=.6, position=position_dodge(0.1)) +
    geom_point(position=position_dodge(0.1)) + 
    scale_x_continuous(breaks = 2008:2018, limits = c(2007,2019) , labels = as.character(c(2008:2018))) +
    scale_y_continuous(breaks = 1:5, limits = c(2,4)) + 
    labs(title = "CDN-size per age", caption = "Note: 95% CI \n Source: CentERdata 2021", 
       y = "CDN size", x="period") + 
   scale_colour_hue(name="age ego",    # Legend label, use darker colors
                    l=40)        +                # Use darker colors, lightness=40
    theme(legend.justification=c(1,0),
          legend.position=c("right"))  

plot
ggplotly(plot) %>%
  layout(margin = list(b=100), annotations = list(x=2017, y = 1.9, showarrow = F, font = list(size=10), text=" \n  \n \n \n \n \n Note: 95% CI \n Source: CentERdata 2021"))

```

# Ethnicity {.tabset .tabset-fade}

```{r}
library(plotly)

library(ggplot2)


ToothGrowth$dose <- as.factor(ToothGrowth$dose)


p <- ggplot(ToothGrowth, aes(x=dose, y=len, fill=dose)) + 

  geom_boxplot()


p <- p + theme(legend.title = element_text(colour="red", size=10, 

                                      face="italic"))

p <- p + theme(legend.text = element_text(colour="blue", size=10, 

                                     face="bold"))


ggplotly(p)


# A different data set
df1 <- data.frame(
    sex = factor(c("Female","Female","Male","Male")),
    time = factor(c("Lunch","Dinner","Lunch","Dinner"), levels=c("Lunch","Dinner")),
    total_bill = c(13.53, 16.81, 16.24, 17.42)
)

# A basic graph
lp <- ggplot(data=df1, aes(x=time, y=total_bill, group=sex, shape=sex)) + geom_line() + geom_point()
lp

# Change the legend
lp + scale_shape_discrete(name  ="Payer",
                          breaks=c("Female", "Male"),
                          labels=c("Woman", "Man"))


```



Try to filter out age effect
```{r}

datajt %>% 
  filter(leeftijd>24 & leeftijd<30) %>%
  group_by(survey_wave, opl4) %>%
  summarise(N = n(),
            cdn_sizeM = mean(cdn_size, na.rm=T),
            sd = sd(cdn_size, na.rm=T)) %>%
  mutate(
    se = sd / sqrt(N) ,
    conf.interval = .95,
    ci = se * qt(conf.interval/2 + .5, N-1)) %>% 
  na.omit() -> tgc



ggplot(tgc, aes(x=as.numeric(survey_wave), y=cdn_sizeM, colour=as.factor(opl4))) + 
    geom_errorbar(aes(ymin=cdn_sizeM-ci, ymax=cdn_sizeM+ci), width=.6, position=position_dodge(0.1)) +
    geom_line(position=position_dodge(0.1)) +
    geom_point(position=position_dodge(0.1)) + 
    scale_x_continuous(breaks = 1:11, limits = c(0,12)) +
    scale_y_continuous(breaks = 1:5, limits = c(1,4)) + 
    labs(title = "CDN-size per education", caption = "Note: 95% CI \n Source: CentERdata 2021", 
       y = "CDN size", x="period") + 
    scale_colour_hue(name="education ego",    # Legend label, use darker colors
                     breaks=c("1", "2", "3", "4"),
                     labels=c("primary + vmbo", "havo/vwo/mbo", "hbo", "university"),
                     l=40)       +              # Use darker colors, lightness=40
    theme(legend.justification=c(1,0),
          legend.position=c(.98,.58))  
```



```{r}
datajt %>% 
  group_by(survey_wave, opl4) %>%
  summarise(N = n(),
            cdn_neduc_hM = mean(cdn_neduc_h, na.rm=T),
            sd = sd(cdn_neduc_h, na.rm=T)) %>%
  mutate(
    se = sd / sqrt(N) ,
    conf.interval = .95,
    ci = se * qt(conf.interval/2 + .5, N-1)) %>% 
  na.omit() -> tgc

ggplot(tgc, aes(x=as.numeric(survey_wave), y=cdn_neduc_hM, colour=as.factor(opl4))) + 
    geom_errorbar(aes(ymin=cdn_neduc_hM-ci, ymax=cdn_neduc_hM+ci), width=.6, position=position_dodge(0.1)) +
    geom_line(position=position_dodge(0.1)) +
    geom_point(position=position_dodge(0.1)) + 
    scale_x_continuous(breaks = 1:11, limits = c(0,12)) +
    scale_y_continuous(breaks = 0:2, limits = c(0,2.8)) + 
    labs(title = "Number of university educated alters \n per education", caption = "Note: 95% CI \n Source: CentERdata 2021", 
       y = "CDN size", x="period") + 
    scale_colour_hue(name="education ego",    # Legend label, use darker colors
                     breaks=c("1", "2", "3", "4"),
                     labels=c("primary + vmbo", "havo/vwo/mbo", "hbo", "university"),
                     l=40)       +              # Use darker colors, lightness=40
    theme(legend.justification=c(1,0),
          legend.position=c(.98,.54))  



```

```{r}
datajt %>% 
  filter(leeftijd>24 & !is.na(opl4)) %>%
  group_by(survey_wave, opl4) %>%
  summarise(N = n(),
            cdn_educ_EIM = mean(educ_EI, na.rm=T),
            sd = sd(educ_EI, na.rm=T),
            cdn_educ_EIM_w = wtd.mean(educ_EI, cdn_size, normwt = FALSE, na.rm = TRUE), #perhaps better to set normwt to TRUE
            sd_w = sqrt(wtd.var(educ_EI, cdn_size, normwt = FALSE, na.rm = TRUE))) %>%
  mutate(
    conf.interval = .95,
    se = sd / sqrt(N) ,
    ci = se * qt(conf.interval/2 + .5, N-1),
    se_w = sd_w / sqrt(N) , #is this correct??
    ci_w = se_w * qt(conf.interval/2 + .5, N-1)) %>%   
  na.omit() -> tgc



datajt_nk %>% 
  filter(leeftijd>24) %>%
  group_by(survey_wave, opl4) %>%
  summarise(N = n(),
            cdn_educ_EIM = mean(educ_EI, na.rm=T),
            sd = sd(educ_EI, na.rm=T)) %>%
  mutate(
    se = sd / sqrt(N) ,
    conf.interval = .95,
    ci = se * qt(conf.interval/2 + .5, N-1)) %>% 
  na.omit() -> tgc_nk

``` 
```{r}

ggplot(tgc, aes(x=as.numeric(survey_wave), y=cdn_educ_EIM, colour=as.factor(opl4))) + 
    geom_errorbar(aes(ymin=cdn_educ_EIM-ci, ymax=cdn_educ_EIM+ci), width=.6, position=position_dodge(0.1)) +
    geom_line(position=position_dodge(0.1)) +
    geom_point(position=position_dodge(0.1)) + 
    scale_x_continuous(breaks = 1:11, limits = c(0,12), labels = as.character(c(2008:2018))) +
    scale_y_continuous(breaks = -1:1, limits = c(-1,1)) + 
    labs(title = "Educational homogeneity in CDN\n per education ", caption = "Note: 95% CI \n Source: CentERdata 2021 \n (own calculations)", 
       y = "EI-index", x="period") + 
    scale_colour_hue(name="education ego",    # Legend label, use darker colors
                     breaks=c("1", "2", "3", "4"),
                     labels=c("primary + vmbo", "havo/vwo/mbo", "hbo", "university"),
                     l=40)       +              # Use darker colors, lightness=40
    theme(legend.justification=c(1,0),
          legend.position="right")  


#legend.position=c(.22,.1))


```

```{r}

ggplot(tgc, aes(x=as.numeric(survey_wave), y=cdn_educ_EIM_w, colour=as.factor(opl4))) + 
    geom_errorbar(aes(ymin=cdn_educ_EIM_w-ci_w, ymax=cdn_educ_EIM_w+ci_w), width=.6, position=position_dodge(0.1)) +
    geom_line(position=position_dodge(0.1)) +
    geom_point(position=position_dodge(0.1)) + 
    scale_x_continuous(breaks = 1:11, limits = c(0,12), labels = as.character(c(2011:2021))) +
    scale_y_continuous(breaks = -1:1, limits = c(-1,1)) + 
    labs(title = "Educational homogeneity \n per education \n weighted by CDN size ", caption = "Note: 95% CI \n Source: CentERdata 2021", 
       y = "EI-index", x="period") + 
    scale_colour_hue(name="education ego",    # Legend label, use darker colors
                     breaks=c("1", "2", "3", "4"),
                     labels=c("primary + vmbo", "havo/vwo/mbo", "hbo", "university"),
                     l=40)       +              # Use darker colors, lightness=40
    theme(legend.justification=c(1,0),
          legend.position="right")  



```


```{r}

ggplot(tgc_nk, aes(x=as.numeric(survey_wave), y=cdn_educ_EIM, colour=as.factor(opl4))) + 
    geom_errorbar(aes(ymin=cdn_educ_EIM-ci, ymax=cdn_educ_EIM+ci), width=.6, position=position_dodge(0.1)) +
    geom_line(position=position_dodge(0.1)) +
    geom_point(position=position_dodge(0.1)) + 
    scale_x_continuous(breaks = 1:11, limits = c(0,12)) +
    scale_y_continuous(breaks = -1:1, limits = c(-1,1)) + 
    labs(title = "Educational homogeneity \n per education \n (older than 24 & nokin)", caption = "Note: 95% CI \n Source: CentERdata 2021", 
       y = "CDN size", x="period") + 
    scale_colour_hue(name="education ego",    # Legend label, use darker colors
                     breaks=c("1", "2", "3", "4"),
                     labels=c("primary + vmbo", "havo/vwo/mbo", "hbo", "university"),
                     l=40)       +              # Use darker colors, lightness=40
    theme(legend.justification=c(1,0),
          legend.position=c(.22,.1))  



```



## Gender  

```{r}

datajt %>% 
  filter(!is.na(geslacht)) %>%
  group_by(survey_wave, geslacht) %>%
  summarise(N = n(),
            cdn_ngender_2M = mean(cdn_ngender_2, na.rm=T),
            sd = sd(cdn_ngender_2, na.rm=T)) %>%
  mutate(
    se = sd / sqrt(N) ,
    conf.interval = .95,
    ci = se * qt(conf.interval/2 + .5, N-1)) -> datac

ggplot(datac, aes(x=as.numeric(survey_wave), y=cdn_ngender_2M, colour=as.factor(geslacht))) + 
    geom_errorbar(aes(ymin=cdn_ngender_2M-ci, ymax=cdn_ngender_2M+ci), width=.6, position=position_dodge(0.1)) +
    geom_line(position=position_dodge(0.1)) +
    geom_point(position=position_dodge(0.1)) + 
    scale_x_continuous(breaks = 1:11, limits = c(0,12), labels = as.character(c(2011:2021))) +
    scale_y_continuous(breaks = 0:3, limits = c(0,3)) + 
    labs(title = "Female confidants \n gender", caption = "Note: 95% CI \n Source: CentERdata 2021", 
       y = "number of female confidants", x="period") + 
    scale_colour_hue(name="gender ego",    # Legend label, use darker colors
                     breaks=c("2", "1"),
                     labels=c("female", "male"),
                     l=40)       +              # Use darker colors, lightness=40
    theme(legend.justification=c(1,0),
          legend.position=c(.98,.68))  
  
```
```{r}
datajt %>% 
  filter(cdn_size>0 & !is.na(geslacht)) %>%
  group_by(survey_wave, geslacht) %>%
  summarise(N = n(),
            gender_EI_mean = mean(gender_EI, na.rm=T),
            sd = sd(gender_EI, na.rm=T)) %>%
  mutate(
    se = sd / sqrt(N) ,
    conf.interval = .95,
    ci = se * qt(conf.interval/2 + .5, N-1)) -> datac

ggplot(datac, aes(x=as.numeric(survey_wave), y=gender_EI_mean, colour=as.factor(geslacht))) + 
    geom_errorbar(aes(ymin=gender_EI_mean-ci, ymax=gender_EI_mean+ci), width=.6, position=position_dodge(0.1)) +
    geom_line(position=position_dodge(0.1)) +
    geom_point(position=position_dodge(0.1)) + 
    scale_x_continuous(breaks = 1:11, limits = c(0,12), labels = as.character(c(2011:2021))) +
    scale_y_continuous(breaks = c(-.5,0,.5), limits = c(-.5,.5)) + 
    labs(title = "Gender homogeneity in CDN \n (EI-index, higher scores more homogeneity)", caption = "Note: 95% CI \n Source: CentERdata 2021", 
       y = "EI-index", x="period") + 
    scale_colour_hue(name="gender ego",    # Legend label, use darker colors
                     breaks=c("2", "1"),
                     labels=c("female", "male"),
                     l=40)       +              # Use darker colors, lightness=40
    theme(legend.justification=c(1,0),
          legend.position="right")  
  

```

```{r}



datajt_nk %>% 
  filter(cdn_size>0 & !is.na(geslacht)) %>%
  group_by(survey_wave, geslacht) %>%
  summarise(N = n(),
            gender_EI_mean = mean(gender_EI, na.rm=T),
            sd = sd(gender_EI, na.rm=T)) %>%
  mutate(
    se = sd / sqrt(N) ,
    conf.interval = .95,
    ci = se * qt(conf.interval/2 + .5, N-1)) -> datac

ggplot(datac, aes(x=as.numeric(survey_wave), y=gender_EI_mean, colour=as.factor(geslacht))) + 
    geom_errorbar(aes(ymin=gender_EI_mean-ci, ymax=gender_EI_mean+ci), width=.6, position=position_dodge(0.1)) +
    geom_line(position=position_dodge(0.1)) +
    geom_point(position=position_dodge(0.1)) + 
    scale_x_continuous(breaks = 1:11, limits = c(0,12)) +
    scale_y_continuous(breaks = c(-.5,0,.5,1), limits = c(0,1)) + 
    labs(title = "gender homophily \n (EI-index, higher scores more homogeneity)", caption = "Note: 95% CI \n Source: CentERdata 2021", 
       y = "gender homophily", x="period") + 
    scale_colour_hue(name="gender ego",    # Legend label, use darker colors
                     breaks=c("1", "2"),
                     labels=c("male", "female"),
                     l=40)       +              # Use darker colors, lightness=40
    theme(legend.justification=c(1,0),
          legend.position=c(.98,.18))  
  


```




## leeftijd

```{r}
datajt %>% 
  filter(!is.na(leeftijd) & leeftijd>24) %>%
  group_by(survey_wave, leeftijd_cat13) %>%
  summarise(N = n(),
            cdn_leeftijd_EIM = mean(leeftijd_EI, na.rm=T),
            sd = sd(leeftijd_EI, na.rm=T),
            cdn_educ_EIM_w = wtd.mean(leeftijd_EI, cdn_size, normwt = FALSE, na.rm = TRUE), #perhaps better to set normwt to TRUE
            sd_w = sqrt(wtd.var(leeftijd_EI, cdn_size, normwt = FALSE, na.rm = TRUE))) %>%
  mutate(
    conf.interval = .95,
    se = sd / sqrt(N) ,
    ci = se * qt(conf.interval/2 + .5, N-1),
    se_w = sd_w / sqrt(N) , #is this correct??
    ci_w = se_w * qt(conf.interval/2 + .5, N-1)) %>%   
  na.omit() -> tgc



datajt_nk %>% 
   filter(!is.na(leeftijd)) %>%
  group_by(survey_wave, leeftijd_cat13) %>%
  summarise(N = n(),
            cdn_leeftijd_EIM = mean(leeftijd_EI, na.rm=T),
            sd = sd(leeftijd_EI, na.rm=T),
            cdn_educ_EIM_w = wtd.mean(leeftijd_EI, cdn_size, normwt = FALSE, na.rm = TRUE), #perhaps better to set normwt to TRUE
            sd_w = sqrt(wtd.var(leeftijd_EI, cdn_size, normwt = FALSE, na.rm = TRUE))) %>%
  mutate(
    conf.interval = .95,
    se = sd / sqrt(N) ,
    ci = se * qt(conf.interval/2 + .5, N-1),
    se_w = sd_w / sqrt(N) , #is this correct??
    ci_w = se_w * qt(conf.interval/2 + .5, N-1)) %>%   
  na.omit() -> tgc_nk
 
``` 
```{r}

test <- cut(as.numeric(liss_long$leeftijd),breaks = c(-Inf, 15, 20, 25, 30, 35, 40,45,50,55,60,65,70, Inf))
#levels(test)

ggplot(tgc_nk, aes(x=as.numeric(survey_wave), y=cdn_leeftijd_EIM, colour=as.factor(leeftijd_cat13))) + 
    geom_errorbar(aes(ymin=cdn_leeftijd_EIM-ci, ymax=cdn_leeftijd_EIM+ci), width=.6, position=position_dodge(0.1)) +
    geom_line(position=position_dodge(0.1)) +
    geom_point(position=position_dodge(0.1)) + 
    scale_x_continuous(breaks = 1:11, limits = c(0,12), labels = as.character(c(2011:2021))) +
    scale_y_continuous(breaks = c(-.5,0,.5), limits = c(-1,.8)) + 
    labs(title = "Age homogeneity \n (EI-index, higher scores more homogeneity)", caption = "Note: 95% CI \n Source: CentERdata 2021", 
       y = "EI-index", x="period") + 
    scale_colour_hue(name="age ego",    # Legend label, use darker colors
                     #breaks=c("1", "2"),
                     labels=levels(test),
                     l=40)       +              # Use darker colors, lightness=40
    theme(legend.justification=c(1,0),
          legend.position="right")  
  
```

## Etnicity

```{r}

datajt %>% 
  filter(!is.na(etni3)) %>%
  group_by(survey_wave, etni3) %>%
  summarise(N = n(),
            cdn_etni_EIM = mean(etni_EI, na.rm=T),
            sd = sd(etni_EI, na.rm=T),
            cdn_etni_EIM_w = wtd.mean(etni_EI, cdn_size, normwt = FALSE, na.rm = TRUE), #perhaps better to set normwt to TRUE
            sd_w = sqrt(wtd.var(etni_EI, cdn_size, normwt = FALSE, na.rm = TRUE))) %>%
  mutate(
    conf.interval = .95,
    se = sd / sqrt(N) ,
    ci = se * qt(conf.interval/2 + .5, N-1),
    se_w = sd_w / sqrt(N) , #is this correct??
    ci_w = se_w * qt(conf.interval/2 + .5, N-1)) %>%   
  na.omit() -> tgc

hist(tgc$cdn_etni_EIM)
```

```{r}
ggplot(tgc, aes(x=as.numeric(survey_wave), y=cdn_etni_EIM, colour=as.factor(etni3))) + 
    geom_errorbar(aes(ymin=cdn_etni_EIM-ci, ymax=cdn_etni_EIM+ci), width=.6, position=position_dodge(0.1)) +
    geom_line(position=position_dodge(0.1)) +
    geom_point(position=position_dodge(0.1)) + 
    scale_x_continuous(breaks = 1:11, limits = c(0,12), labels = as.character(c(2008:2018))) +
    scale_y_continuous(breaks = c(-1,-.5,0,.5,1), limits = c(-1,1)) + 
    labs(title = "Etnic homogeneity \n (EI-index, higher scores more homogeneity)", caption = "Note: 95% CI \n Source: CentERdata 2021", 
       y = "EI-index", x="period") + 
    scale_colour_hue(name="etni ego",    # Legend label, use darker colors
                     #breaks=c("1", "2"),
                     labels=c("D", "W", "NW"),
                     l=40)       +              # Use darker colors, lightness=40
    theme(legend.justification=c(1,0),
          legend.position="right")  
```





## Take Home Message  

- Partners influence each others opinions.
  - React to shocks  
  - Convergence  
- Influence just as strong for men/women.  

---  


## References
